%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\usepackage{bibentry}
\bibliographystyle{unsrt}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}
\nocite{*}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Jacob Jeffries}}}} % First name
	
	\vspace{6pt}
	
	{\Large Graduate Student} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
    \icon{MapMarker}{11}{Clemson, SC, USA}\\
    \icon{Github}{11}{\href{https://github.com/jwjeffr}{github.com/jwjeffr}}\\
	
\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
		
    \icon{Envelope}{11}{\href{mailto:jwjeffries2000@gmail.com}{jwjeffries2000 (at) gmail (dot) com}}\\
    \icon{LinkedinSquare}{11}{\href{https://www.linkedin.com/in/jjeffries12}{linkedin.com/in/jjeffries12}}\\    
    
\end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.46\textwidth}
    \cvsect{Summary}
	\vspace{-6pt}
 
    %Dummy text
	Ph.D. student in materials science and engineering focused on multi-scale modeling, high-performance computing, molecular dynamics, Monte Carlo methods, and applied physics. \\
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
    \cvsect{Skills}
    \vspace{-6pt}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
    Python, Julia, MATLAB, R, \LaTeX, C++, C.  
    \end{minipage}
    \vspace{4mm}

    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Packages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
    OVITO, PyTorch, NumPy, jax, Numba, pandas, polars, SQLALchemy, scipy
    \end{minipage}
    \vspace{4mm}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Softwares:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
    LAMMPS, OVITO, VASP
    \end{minipage}
    \vspace{1mm}
    
\end{minipage}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
    \entry
        {Python}
        {Diffusion in rough potential energy landscapes}
        {}
        {Analytical statistical mechanics and Kinetic Monte Carlo simulations to quantify diffusion on a rough potential energy surface.}
    \entry
        {LAMMPS \\ Python \\ R}
        {Chemical potential calculator}
        {\href{https://github.com/jwjeffr/chemical_potential_bulk}{github.com}}
        {LAMMPS interface to calculate and fit chemical potentials of random solid solutions.}
    \entry
		{LAMMPS \\ Python}
		{Impurity concentration in concentrated alloys}
        {\href{https://github.com/jwjeffr/vacancy_concentration}{github.com}/\href{https://arxiv.org/abs/2402.07324}{arXiv}}
		{$\mu pT$ pseudo-ensemble model for impurity concentration in concentrated alloys.}
    \entry
        {PyTorch \\ Python}
		{Kinetic Monte Carlo crystal growth}
        {\href{https://github.com/jwjeffr/pytorch_kmc}{github.com}}
		{Density functional theory-informed Kinetic Monte Carlo simulations of crystal growth of pentaerythritol tetranitrate and $\beta$-1,3,5,7-tetranitro-1,3,5,7-tetrazoctane.}
    \entry
		{PyTorch \\ Python}
		{Quadratic unconstrained binary optimization annealing}{\href{https://github.com/jwjeffr/pytorch_annealing}{github.com}}
		{Metropolis annealing for solving the QUBO problem.}
    \entry
		{PyTorch \\ Python}
		{Portable cluster expansion fitting}
		{\href{https://github.com/jwjeffr/cluster_expansion_pytorch}{github.com}}
		{Constrained cluster expansion fitting using PyTorch and cooper.}
    \entry
		{OVITO \\ Python}
		{Cowley short-range order parameter modifier}
		{\href{https://github.com/jwjeffr/cowley_sro_parameters}{github.com}/\href{https://pypi.org/project/cowley-sro-parameters/}{pypi.org}}
		{Custom OVITO modifier for calculating the Cowley short-range order parameter during a molecular dynamics run.}
    \entry
		{OVITO \\ Python}
		{Onsager coefficients calculator}
		{\href{https://github.com/jwjeffr/onsager_coefficients/}{github.com}/\href{https://pypi.org/project/cowley-sro-parameters/}{pypi.org}}
		{Repository for calculating Onsager coefficients from a molecular dynamics run, including a general-purpose particle-reduction OVITO modifier.}
    \entry
		{SciPy \\ Python}
		{Optimal color palette generator}
		{\href{https://github.com/jwjeffr/optcolpal}{github.com}}
		{Color palette generator that maximizes pairwise CIELAB distance between colors in the palette.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
    \entry
		{2023 - }
		{Materials Science and Engineering (Ph.D.)}
		{Clemson University}
		{Computational multi-scale materials science for concentrated alloys, materials under extreme conditions, and nuclear materials. Focus on molecular dynamics and Monte Carlo methods.}
    \entry
		{2019 - 2022}
		{Physics (B.S.), Magna Cum Laude}
		{Clemson University}
		{Minors in chemistry and mathematics, honors distinctions in physics and chemistry.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Experience}
\begin{entrylist}
	\entry
        {2023 -}
		{Graduate Research Assistant}
		{Department of Materials Science and Engineering, Clemson University}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Atomistic simulations of concentrated alloys on high performance computers.
            \begin{itemize}%[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=0pt]
                \item Molecular dynamics simulations of point-defect hopping.
                \item Thermodynamics of point defects using molecular statics.
                \item Molecular dynamics-informed phase-field simulations of radiation-induced segregation.
            \end{itemize}
            \item Kinetic Monte Carlo simulations of vacancy hopping on rough potential energy surfaces.
        \end{itemize} 
        }
	\entry
		{2023 --}
		{Graduate Student}
		{T1 Division, Los Alamos National Laboratory}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item GPU-accelerated Kinetic Monte Carlo simulations of organic crystal growth from solution using density functional tight binding bond energies on high-performance computers using PyTorch.
            \item GPU-accelerated quadratic unconstrained binary optimization for organic crystal equilibrium shapes using simulated annealing with PyTorch.
        \end{itemize} 
        }
	\entry
		{2022 -- 2022}
		{Undergraduate Intern}
		{University of Maryland, College Park}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Reservoir computing machine learning framework to predict national and state-level COVID-19 trends using the rescompy library.
        \end{itemize} 
        }
    \entry
		{2022 -- 2022}
		{Undergraduate Researcher}
		{Department of Materials Science and Engineering, Clemson University}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Non-equilibrium molecular dynamics simulations of vacancy hopping in tungsten on high-performance computers.
            \item Molecular dynamics simulations of point-defect hopping in iron-based concentrated alloys on high-performance computers.
        \end{itemize} 
        }
    \entry
		{2021 -- 2022}
		{Undergraduate Researcher}
		{Department of Chemistry, Clemson University}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Analysis of short-term chaos and long-term pseudo-random-number-generator-induced synchronization in the Langevin equation on rough potential energy surfaces.
        \end{itemize} 
        }
    \entry
		{2019 -- 2022}
		{Undergraduate Researcher}
		{Department of Physics and Astronomy, Clemson University}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Computational bioinformatics and protein thermodynamics on high-performance computers focused on targeted medicine.
        \end{itemize}
        }
\end{entrylist}

\vspace{-10 pt}
\renewcommand\refname{}
\cvsect{Publications}
\vspace{-1.5cm}
\bibliography{ref}

\cvsect{Conferences}
\begin{entrylist}
    \entry
        {2021 \\ \color{gray} \textit{Virtual}}
        {American Chemical Society Spring Virtual National Meeting}
        {}
        {Oral presentation on instabilities of melanosome proteins (OCA2, SLC45A2, TYR, TPC2, and ATP7A) from point mutations and implication for disease}
    \entry
        {2024 \\ \color{gray} \textit{Kingston, Ontario}}
        {The 16th conference of COmputer Simulation of IRradiation Effects in Solids}
        {}
        {Oral presentation on diffusivity of vacancies on a noisy potential energy surface}
\end{entrylist}

\end{document}
